Interval Probability for Fuzzy Quantum Theories

### 2016-06-24 prob.tex
prob.tex \subsection{Quantum Events} updates...

@@

\begin{definition}[Ideal Measurement; Complement;
Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}

@@

For a given set of events $\events$, there are many possible probability
measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
a postulate of quantum mechanics, states that each pure quantum state
$\ket{\phi}$ induces a probability measure $\mu^B_{\phi}$
as follows: 
\[
\mu^B_{\phi}(P)=\ip{\phi}{P\phi}
\]

Moreover, the Born rule can be extended to a mixed state. Suppose
we want to prepare a quantum system. As we discussed in classical
probability, our ability of preparing a state might not be prefect.
If we want to prepare $\ket{\phi}$, we may turn out preparing a set
of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$. Then,
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu^B_{\phi_{j}}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$,
for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
an unique mixed state~$\rho$ such that $\mu=\mu^B_{\rho}$.\end{cor}

>>>>

Based on quantum events are projection operators, operations and properties of
quntum events can be written in terms of those of operators.

\begin{definition}[Ideal Measurement; Complement;
Commutativity~\cite{Swart2013,peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item A set of mutually orthogonal projections $P_{i}$ is called an \emph{ideal
measurement} if it is a partition of the identity, i.e.,
$\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}=\mathbb{1}$.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal to $P$,
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}

@@

@@

For a given set of events $\events$, there are many possible probability
measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
a postulate of quantum mechanics, states that each pure normalized
($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$ induces a probability measure
$\mu^B_{\phi}$ as follows: 
\[
\mu^B_{\phi}(P)=\ip{\phi}{P\phi}
\]

Moreover, the Born rule can be extended to a mixed state. Suppose
we want to prepare a quantum system. As we discussed in classical
probability, our ability of preparing a state might not be perfect.
If we want to prepare $\ket{\phi}$, we may turn out preparing a set
of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$. Then,
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu^B_{\phi_{j}}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of dimension
$d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
an unique mixed state~$\rho$ such that $\mu=\mu^B_{\rho}$.\end{cor}
